---
title: "Colorado State University Interactive Map"
author: "HaiyanChen"
date: "2026-04-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview
This project creates an interactive map of Colorado State University. The map visualizes selected locations, including residence halls, the Department of Environmental and Radiological Health Sciences (ERHS), Morgan Library, Curfman Gallery, and the CSU Health and Medical Center. Different categories of locations are displayed using different colors to improve visual interpretation.


```{r echo = FALSE}
setwd("E:/新技能/Epidemiology/John_Hopkins_Developing_Data_Products")
# Prepare the latitude and longitude for locations
# Create a data frame of CSU locations
csu_points <- data.frame(
    name = c(
        "Academic Village",
        "Allison Hall",
        "Braiden Hall",
        "Corbett Hall",
        "Durward Hall",
        "Edwards Hall",
        "Ingersoll Hall",
        "Laurel Village",
        "Newsom Hall",
        "Parmelee Hall",
        "Summit Hall",
        "Westfall Hall",
        "ERHS (Environmental and Radiological Health Sciences)",
        "Morgan Library",
        "Curfman Gallery",
        "CSU Health and Medical Center"
    ),
    
    lat = c(
        40.57229873780172,
        40.577516412251,
        40.571804112705706,
        40.5772034646794,
        40.57771340136919,
        40.57193011056468,
        40.57203135606741,
        40.59651617661135,
        40.57183166219014,
        40.57730509773882,
        40.57049051574559,
        40.5773778998063,
        40.56921445699542,
        40.5733053548333,
        40.57423186205259,
        40.56836371306185
    ),
    
    lng = c(
        -105.09025109285038,
        -105.08550190207693,
        -105.08556959042771,
        -105.09008520392229,
        -105.09317534625215,
        -105.09271571741739,
        -105.09469442664427,
        -105.09153954856284,
        -105.08905084071641,
        -105.08909270392229,
        -105.0932993671289,
        -105.09411310392237,
        -105.0822237892409,
        -105.08469658858232,
        -105.08467347897388,
        -105.0777932732809
    ),
    
    # Group each location by type
    type = c(
        rep("dorm", 12),
        "college",
        "library",
        "gallery",
        "medical"
    )
)

library(leaflet)

# Build the base map
CSU_school_map <- leaflet(csu_points) %>%
    addProviderTiles(providers$CartoDB.Positron) %>%
    
    # Add clustered dorm locations
    addCircleMarkers(
        data = subset(csu_points, type == "dorm"),
        lng = ~lng,
        lat = ~lat,
        color = "#2E86DE",
        fillColor = "#2E86DE",
        fillOpacity = 0.85, # Set marker transparency
        radius = 7, # Set marker size
        stroke = TRUE,  # Add a border around each marker
        weight = 1,  # Set border thickness
        popup = ~paste0("<b>", name, "</b><br/>Type: ", type), # Show name and type in popup
        label = ~name,  # Show location name on hover
        clusterOptions = markerClusterOptions() # Cluster nearby markers
    ) %>%
    
    # Add clustered college location
    addCircleMarkers(
        data = subset(csu_points, type == "college"),
        lng = ~lng,
        lat = ~lat,
        color = "#E74C3C",
        fillColor = "#E74C3C",
        fillOpacity = 0.85,
        radius = 7,
        stroke = TRUE,
        weight = 1,
        popup = ~paste0("<b>", name, "</b><br/>Type: ", type),
        label = ~name,
        clusterOptions = markerClusterOptions()
    ) %>%
    
    # Add clustered library location
    addCircleMarkers(
        data = subset(csu_points, type == "library"),
        lng = ~lng,
        lat = ~lat,
        color = "#27AE60",
        fillColor = "#27AE60",
        fillOpacity = 0.85,
        radius = 7,
        stroke = TRUE,
        weight = 1,
        popup = ~paste0("<b>", name, "</b><br/>Type: ", type),
        label = ~name,
        clusterOptions = markerClusterOptions()
    ) %>%
    
    # Add clustered gallery location
    addCircleMarkers(
        data = subset(csu_points, type == "gallery"),
        lng = ~lng,
        lat = ~lat,
        color = "#8E44AD",
        fillColor = "#8E44AD",
        fillOpacity = 0.85,
        radius = 7,
        stroke = TRUE,
        weight = 1,
        popup = ~paste0("<b>", name, "</b><br/>Type: ", type),
        label = ~name,
        clusterOptions = markerClusterOptions()
    ) %>%
    
    # Add clustered medical location
    addCircleMarkers(
        data = subset(csu_points, type == "medical"),
        lng = ~lng,
        lat = ~lat,
        color = "#F39C12",
        fillColor = "#F39C12",
        fillOpacity = 0.85,
        radius = 7,
        stroke = TRUE,
        weight = 1,
        popup = ~paste0("<b>", name, "</b><br/>Type: ", type),
        label = ~name,
        clusterOptions = markerClusterOptions()
    ) %>%
    
    # Add a legend for location types
    addLegend(
        position = "bottomright",
        colors = c("#2E86DE", "#E74C3C", "#27AE60", "#8E44AD", "#F39C12"),
        labels = c("dorm", "college", "library", "gallery", "medical"),
        title = "CSU Location Types",
        opacity = 1
    )

# Save document
htmlwidgets::saveWidget(CSU_school_map, "map.html", selfcontained = TRUE)

```
